Brownian Dynein Model

### 2016-06-14 latex/paper.tex
Add bit to paper.tex on why we do not need to treat negative L values any different from positive ones.

>>>>

The only change between the near and far coordinates (other than switching $L_n$ and $L_f$) is the
sign of $\cos\theta_{n/f}$. This is because, for positive L, $\theta_n$ is an internal angle and
$\theta_f$ is an external angle to the $L-L_n-L_f$ triangle. To properly deal with the $\theta_f$
angle, we must use its complement: $\pi - \theta_f$. The sign switch is because
$\cos\left(\pi - \theta_f\right) = -\cos\theta_f$.\\

For negative L values, the only change to the model is that $\theta_n$ becomes an external angle and
$\theta_f$ becomes internal. As we know, we must introduce a sign shift to account for this.
However we do not need to do any extra work, since the L in the denominator of $\cos\theta_f$
provides the necessary sign shift for $\theta_n$ going from internal to external.
